### 2016-12-15 local-capability-machine.tex
changed configuration has stack to reg points to stack.
changed conclusion of scall lemma to take stack into account
typo in cnst region def
scall lemma: added unused to conclusion of Hyp-Cont
Updated scall works Hyp-Cont to work better

\begin{align*}
  \iota^\cnst (v,n) &= (v,1,=,H^\cnst\;n)\\
  H^\sta \; n \; s \; \hat{W} = & \{\npair{\ms} \mid n > 0 \Rightarrow \forall a \in \dom(\ms)\ldotp \ms(a) = n \}
\end{align*}

@@

\begin{definition}
  We say that $(\reg,\ms) \text{ is looking at } [i_0,\cdots,i_n] \text{ followed by } c_{\mathit{next}}$ if
  \begin{itemize}
  \item $\reg(\pcreg) = ((p,g),b,e,a)$
  \item $p = \rwx$, $p = \exec$, or $p = \rwlx$
  \item $a+n\leq e$, $b\leq a\leq e$
  \item $\ms(a+0,\cdots,a+n) = [i_0,\cdots,i_n]$
  \item $c_{\mathit{next}} = ((p,g),b,e,a+n+1)$
  \end{itemize}
\end{definition}

\begin{definition}
  $(\reg,\ms) \text{ has stack $\ms_\stk$ with $\ms_{\mathit{unused}}$ unused}$

  \begin{itemize}
  \item $\reg(r_\stk) =((\rwlx,\_),b_\stk,e_\stk,a_\stk)$
  \item $\dom(\ms_{\mathit{unused}}) = [a_\stk+1,\cdots,e_\stk]$
  \item $\dom(\ms_\stk) = [b_\stk,\cdots,a_\stk]$
  \item $b_\stk - 1\leq a_\stk$
  \end{itemize}
\end{definition}

\begin{lemma}[$\mathtt{scall}$ works]
  If
  \begin{itemize}
  \item $\heapSat[\ms]{n}{W}$ 
  \item $(\reg,\ms) \text{ is looking at }
    \mathtt{scall}(r(\overline{r_{\mathit{arg}}},
    \overline{r_{\mathit{priv}}})) \text{ followed by } c_{\mathit{next}}$
  \item $(\reg,\ms) \text{ has stack $\ms_\stk$ with $\ms_{\mathit{unused}}$ unused}$
  \item[Hyp-Callee] If
    \begin{itemize}
    \item $\ms_{\mathit{unused}} = \ms_{\mathit{act}}
      \uplus \ms_{\mathit{unused}}'$,
    \item $W' =
      \revokeTemp{W}[\iota^{\sta}(\temp,\ms_\stk\uplus\ms_{\mathit{act}}),\iota^{\pwl}(\dom(\ms_{\mathit{unused}}'))]$,
    \item $\memSat[n-1]{\ms''}{W'}$
    \item $(\reg',\ms'') \text{ has stack $\emptyset$ with
        $\ms_{\mathit{unused}}'$ unused}$
    \item $\forall a \in \dom(\ms_{\var{unused}}') \ldotp \ms''(a) = 0$
    \item $\reg'= \reg_0[\pcreg\mapsto\updatePcPerm{\reg(r)},
      \overline{r_{\mathit{arg}}} \mapsto \reg(\overline{r_{\mathit{arg}}}),r_0
      \mapsto c_{\mathit{ret}}, r_\stk \mapsto \_]$ 
    \item $(n,c_{\mathit{ret}}) \in \stdvr(W')$
    \end{itemize}
    then we have that $(n-1,(\reg',\ms'')) \in \observations(W')$
  \item[Hyp-Cont] If
    \begin{itemize}
    \item $n' \leq n-2$
    \item $W'' \futurewk \revokeTemp{W}[\iota^{\sta}(\temp,\ms_\stk)]$
    \item for all $r$, we have that:
      \begin{equation*}
        \reg'(r)
        \begin{cases}
          = c_{\mathit{next}} &\text{ if } r = \pcreg\\
          = \reg(r)&\text{ if } r \in \overline{r_{\mathit{priv}}}\\
          \in \stdvr(W'') &\text{ if $\reg'(r)$ is a global capability and } r \not\in \{\pcreg,\overline{r_{\mathit{priv}}}, r_\stk\}
        \end{cases}
      \end{equation*}
    \item $(\reg',\ms'')$ has stack $\ms_\stk$ with
        $\ms_{\mathit{unused}}''$ unused for some $\ms_{\mathit{unused}}''$
    \item $\memSat[n']{\ms''}{W''}$ 
    \end{itemize}
    then we have that $(n', (\reg',\ms'')) \in \observations(W'')$
  \end{itemize}
  Then 
  \begin{itemize}
    \item $(\reg,\ms) \in \observations(W)$
  \end{itemize}

@@

>>>>

\begin{align*}
  \iota^\cnst (v,n) &= (v,1,=,H^\cnst\;n)\\
  H^\cnst \; n \; s \; \hat{W} = & \{\npair{\ms} \mid n > 0 \Rightarrow \forall a \in \dom(\ms)\ldotp \ms(a) = n \}
\end{align*}

@@

\begin{definition}
  We say that $(\reg,\ms) \text{ is looking at } [i_0,\cdots,i_n] \text{ followed by } c_{\mathit{next}}$ 
  iff
  \begin{itemize}
  \item $\reg(\pcreg) = ((p,g),b,e,a)$
  \item $p = \rwx$, $p = \exec$, or $p = \rwlx$
  \item $a+n\leq e$, $b\leq a\leq e$
  \item $\ms(a+0,\cdots,a+n) = [i_0,\cdots,i_n]$
  \item $c_{\mathit{next}} = ((p,g),b,e,a+n+1)$
  \end{itemize}
\end{definition}

\begin{definition}
  We say that $\reg \text{ points to stack with $\ms_\stk$ used and $\ms_{\mathit{unused}}$ unused}$
  iff
  \begin{itemize}
  \item $\reg(r_\stk) =((\rwlx,\_),b_\stk,e_\stk,a_\stk)$
  \item $\dom(\ms_{\mathit{unused}}) = [a_\stk+1,\cdots,e_\stk]$
  \item $\dom(\ms_\stk) = [b_\stk,\cdots,a_\stk]$
  \item $b_\stk - 1\leq a_\stk$
  \end{itemize}
\end{definition}

\begin{lemma}[$\mathtt{scall}$ works]
  If
  \begin{itemize}
  \item $\heapSat[\ms]{n}{W}$ 
  \item $(\reg,\ms) \text{ is looking at }
    \mathtt{scall}(r(\overline{r_{\mathit{arg}}},
    \overline{r_{\mathit{priv}}})) \text{ followed by } c_{\mathit{next}}$
  \item $\reg \text{ points to stack with $\ms_\stk$ used and $\ms_{\mathit{unused}}$ unused}$
  \item[Hyp-Callee] If
    \begin{itemize}
    \item $\ms_{\mathit{unused}} = \ms_{\mathit{act}}
      \uplus \ms_{\mathit{unused}}'$,
    \item $W' =
      \revokeTemp{W}[\iota^{\sta}(\temp,\ms_\stk\uplus\ms_{\mathit{act}}),\iota^{\pwl}(\dom(\ms_{\mathit{unused}}'))]$,
    \item $\memSat[n-1]{\ms''}{W'}$
    \item $\reg' \text{ points to stack with $\emptyset$ used and $\ms_{\mathit{unused}'}$ unused}$
    \item $\forall a \in \dom(\ms_{\var{unused}}') \ldotp \ms''(a) = 0$
    \item $\reg'= \reg_0[\pcreg\mapsto\updatePcPerm{\reg(r)},
      \overline{r_{\mathit{arg}}} \mapsto \reg(\overline{r_{\mathit{arg}}}),r_0
      \mapsto c_{\mathit{ret}}, r_\stk \mapsto \_]$ 
    \item $(n,c_{\mathit{ret}}) \in \stdvr(W')$
    \end{itemize}
    then we have that $(n-1,(\reg',\ms'')) \in \observations(W')$
  \item[Hyp-Cont] If
    \begin{itemize}
    \item $n' \leq n-2$
    \item $W'' \futurewk \revokeTemp{W}[\iota^{\sta}(\temp,\ms_\stk)]$
    \item $\memSat[n']{\ms''}{\revokeTemp{W''}}$ 
    \item for all $r$, we have that:
      \begin{equation*}
        \reg'(r)
        \begin{cases}
          = c_{\mathit{next}} &\text{ if } r = \pcreg\\
          = \reg(r)&\text{ if } r \in \overline{r_{\mathit{priv}}}\\
          \in \stdvr(W'') &\text{ if $\reg'(r)$ is a global capability and } r \not\in \{\pcreg,\overline{r_{\mathit{priv}}}, r_\stk\} %revokeTemp here?
        \end{cases}
      \end{equation*}
    \item $\reg \text{ points to stack with $\ms_\stk$ used and $\ms_{\mathit{unused}}''$ unused}$ for some $\ms_{\mathit{unused}}''$
    \end{itemize}
\lau{Try to extract the ``private stack'' part, so it does not become a proof obligation in the proof that applies this lemma.}

    then we have that $(n', (\reg',\ms'' \uplus \ms_\stk \uplus \ms_{\var{unused}}'')) \in \observations(W'')$
  \end{itemize}
  Then 
  \begin{itemize}
    \item $(\reg,\ms \uplus \ms_\stk \uplus \ms_{\var{unused}}) \in \observations(W)$
  \end{itemize}

@@

\begin{lemma}[Execution and $\observations$]
  \begin{align*}
    & \forall n,i,\reg, \reg', \ms, \ms', \ms_r, W \ldotp\\
    & \quad (\forall \ms_f \ldotp (\reg,\ms \uplus \ms_r \uplus \ms_f) \step[i] (\reg',\ms' \uplus \ms_r \uplus \ms_f)) \land \npair[n-i]{(\reg',\ms')} \in \observations(W) \\
    & \qquad \Rightarrow \npair{(\reg,\ms \uplus \ms_r)} \in \observations(W)
  \end{align*}
